ZCB Pricing

### 2018-08-01 ZCB Pricing .Rmd
Stability changes

A=NULL
B=NULL
C=NULL

for( i in 1:100){
  A[i]=Crude_Monte_Carlo()
  B[i]=Antithetic_variates()
  C[i]=Moment_Matching()
}

@@

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r)
}

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr

@@

A=NULL
B=NULL
C=NULL
D=NULL

for (i in 1:100){
  A[i]=Crude_Monte_Carlo()
  B[i]=Antithetic_variates()
  C[i]=Moment_Matching()
  D[i]=Control_Variates_estimate()
}

@@

>>>>

@@

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
  h <- sqrt(beta^(2)+2*sigma^(2))
  A <-(2*h*exp((beta+h)*(T-t)/2)/(2*h+(beta+h)*(exp((T-t)*(h))-1)))^((2*alpha)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(beta+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r)
}

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr

@@

bond_price()
Control_Variates_estimate()
```

@@

CR=NULL
AN=NULL
MM=NULL
CV=NULL

for ( i in 1:100){
  CR[i]=Crude_Monte_Carlo()
  #AN[i]=Antithetic_variates()
  #MM[i]=Moment_Matching()
  CV[i]=Control_Variates_estimate()
}
